Bird beak's elaboration and innovation

### 2023-04-11 Analysis/06-Figure_with_correlations.Rmd
Update 06-Figure_with_correlations.Rmd

```{r, eval = TRUE, echo = TRUE}
## Calculate the correlations for the projections onto the phylo axis
super_phylo_cor <- get.correlations(results$super_results_phylo)

## Calculate the correlations for the projections onto the group' axes
super_group_cor <- get.correlations(results$super_results_within, exclude.phylo = TRUE)
```

@@

```{r, eval = TRUE, echo = FALSE}
## Calculate the correlations for the projections onto the phylo axis
suborder_phylo_cor <- get.correlations(results$suborder_results_phylo)

## Calculate the correlations for the projections onto the group' axes
suborder_group_cor <- get.correlations(results$suborder_results_within, exclude.phylo = TRUE)
```

>>>>

```{r, eval = TRUE, echo = TRUE}
## Calculate the correlations for the projections onto the phylo axis
super_phylo_cor <- get.correlations.plot(results$super_results_phylo)

## Calculate the correlations for the projections onto the group' axes
super_group_cor <- get.correlations.plot(results$super_results_within, exclude.phylo = TRUE)
```

## Get the correlation fable

y axis = levels
column 1 = correlation of e/i projected on the mega level
column 2 = correlation of e/i projected on the macro level
stars for significant correlation between means.

```{r, echo = TRUE, eval = TRUE}
## Get all the correlations for all the clades
cor_mega_level <- get.correlations.scores(results$super_results_phylo)
cor_macro_level <- get.correlations.scores(results$super_results_within)

## Get the colours
load("../Data/Processed/tip_colours_super_orders.rda")
super_orders_col <- c(tip_colours_super_orders, "phylogeny" = "grey")

## Plot the correlations
pdf("../Manuscript/Figures/correlations_fable.pdf")
par(mfrow = c(1,2))
par(mar = c(5, 8, 4, 0) + 0.1, bty = "n") # c(bottom, left, top, right)
plot.cor.scores(cor_mega_level, col = super_orders_col,
                y.axis = TRUE, plot.phylo = TRUE,
                main = "Elaboration and innovation\nat the mega level") 
par(mar = c(5, 2, 4, 6) + 0.1, bty = "n") # c(bottom, left, top, right)
plot.cor.scores(cor_macro_level, col = super_orders_col,
                y.axis = FALSE, plot.phylo = FALSE,
                main = "Elaboration and innovation\nat the macro level")
dev.off()
```

@@

```{r, eval = TRUE, echo = FALSE}
## Calculate the correlations for the projections onto the phylo axis
suborder_phylo_cor <- get.correlations.plot(results$suborder_results_phylo)

## Calculate the correlations for the projections onto the group' axes
suborder_group_cor <- get.correlations.plot(results$suborder_results_within, exclude.phylo = TRUE)
```
